---
output:
html_document:
self_contained: false
lib_dir: "libs"
fig_height: 2
fig_width: 4
params:
element: "biodiversity"
---

```{r, echo=FALSE, message=F, warning=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F)
library(infographiq)
```

<base target="_parent">
In 2015 there was the highest observed species richness and diversity over the 25 year history of the survey. Forage groups typically found in years with different oceanographic regimes, all co-occurred in 2015 along with influx of tropical species


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/fish/Fish_diversity_richness.csv",
        title   = "Richness of All Forage Taxa",
        y_label = "Average Species Richness (number of species)",
        col_t   = "year",
        col_y   = "ALLRich"
        #skip_lines
        #group_by  
        #std_err   
        #filter
    ),
    error = function(e) e
)
```


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/fish/Fish_diversity_richness.csv",
        title   = "Richness of Juvenile Rockfish and Groundfish (53 taxa)",
        y_label = "Average Species Richness (number of species)",
        col_t   = "year",
        col_y   = "YOYRich"
        #skip_lines
        #group_by  
        #std_err   
        #filter
    ),
    error = function(e) e
)
```


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/fish/Fish_diversity_richness.csv",
        title   = "Richness of Other Forage (49 Taxa)",
        y_label = "Average Species Richness (number of species)",
        col_t   = "year",
        col_y   = "FORRich"
        #skip_lines
        #group_by  
        #std_err   
        #filter
    ),
    error = function(e) e
)
```


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/fish/Fish_diversity_richness.csv",
        title   = "Diversity of all Forage (111 taxa)",
        y_label = "Diversity (Shannon-Weaver)",
        col_t   = "year",
        col_y   = "ALLDiv"
        #skip_lines
        #group_by  
        #std_err   
        #filter
    ),
    error = function(e) e
)
```
The Fisheries Ecology Division (FED, https://swfsc.noaa.gov/GroundfishAnalysis/) of the Southwest Fisheries Science Center (SWFSC)  midwater trawl survey off central California. The data may be used and redistributed for free but is not intended
for legal use, since it may contain inaccuracies. Neither the data
Contributor, ERD, NOAA, nor the United States Government, nor any
of their employees or contractors, makes any warranty, express or
implied, including warranties of merchantability and fitness for a
particular purpose, or assumes any legal liability for the accuracy,
completeness, or usefulness, of this information. Fisheries Ecology Division/SWFSC/NOAA
