---
output:
html_document:
self_contained: false
lib_dir: "libs"
fig_height: 2
fig_width: 4
params:
element: "forage-fish"
---

```{r, echo=FALSE, message=F, warning=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F)
library(infographiq)
```

<base target="_parent">
Forage species form dense schools or aggregations, and when present in high abundance are important food for large predators such as sharks, sea lions, whales, and seabirds. When in low abundance the local health and abundance of predators may be reduced. Values are given for young of the year (YOY) or adult populations.
Though present in the area, some key forage species, such as anchovy, had low abundance patterns leading to impacts to their predators.


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "http://oceanview.pfeg.noaa.gov/erddap/tabledap/cciea_EI_FBC.csvp?time%2Cspecies_group%2Cmean_cpue%2CSeup%2CSelo&distinct()",
        title   = "Adult Northern Anchovy (<i>Engraulis mordax</i>) Abundance off Central California",
        y_label = "Average Abundance catch per unit effort (ln(catch+1))",
        col_t   = "time (UTC)",
        col_y   = "mean_cpue (ln(catch+1))"
        #skip_lines
        #group_by  
        #std_err   
        , filter="species_group == \"Adult anchovy\""
    ),
    error = function(e) e
)
```
Though present in the area, some key forage species, such as anchovy, had low abundance patterns leading to impacts to their predators.


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "http://oceanview.pfeg.noaa.gov/erddap/tabledap/cciea_EI_FBC.csvp?time%2Cspecies_group%2Cmean_cpue%2CSeup%2CSelo&distinct()",
        title   = "YOY Northern Anchovy (<i>Engraulis mordax</i>) Abundance off Central California",
        y_label = "Average Abundance catch per unit effort (ln(catch+1))",
        col_t   = "time (UTC)",
        col_y   = "mean_cpue (ln(catch+1))"
        #skip_lines
        #group_by  
        #std_err   
        , filter="species_group == \"YOY anchovy\""
    ),
    error = function(e) e
)
```


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "http://oceanview.pfeg.noaa.gov/erddap/tabledap/cciea_EI_FBC.csvp?time%2Cspecies_group%2Cmean_cpue%2CSeup%2CSelo&distinct()",
        title   = "Adult Pacific Sardine (<i>Sardinops sagax</i>) Abundance off Central California",
        y_label = "Average Abundance catch per unit effort (ln(catch+1))",
        col_t   = "time (UTC)",
        col_y   = "mean_cpue (ln(catch+1))"
        #skip_lines
        #group_by  
        #std_err   
        , filter="species_group == \"Adult sardine\""
    ),
    error = function(e) e
)
```


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "http://oceanview.pfeg.noaa.gov/erddap/tabledap/cciea_EI_FBC.csvp?time%2Cspecies_group%2Cmean_cpue%2CSeup%2CSelo&distinct()",
        title   = "YOY Pacific Sardine (<i>Sardinops sagax</i>) Abundance off Central California",
        y_label = "Average Abundance catch per unit effort (ln(catch+1))",
        col_t   = "time (UTC)",
        col_y   = "mean_cpue (ln(catch+1))"
        #skip_lines
        #group_by  
        #std_err   
        , filter="species_group == \"YOY sardine\""
    ),
    error = function(e) e
)
```


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "http://oceanview.pfeg.noaa.gov/erddap/tabledap/cciea_EI_FBC.csvp?time%2Cspecies_group%2Cmean_cpue%2CSeup%2CSelo&distinct()",
        title   = "YOY Rockfish Juveniles (<i>YOY rockfish spp.</i>) Abundance off Central California",
        y_label = "Average Abundance catch per unit effort (ln(catch+1))",
        col_t   = "time (UTC)",
        col_y   = "mean_cpue (ln(catch+1))"
        #skip_lines
        #group_by  
        #std_err   
        , filter="species_group == \"YOY rockfish\""
    ),
    error = function(e) e
)
```


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "http://oceanview.pfeg.noaa.gov/erddap/tabledap/cciea_EI_FBC.csvp?time%2Cspecies_group%2Cmean_cpue%2CSeup%2CSelo&distinct()",
        title   = "YOY Pacific Hake  (<i>Merluccius productus</i>) Abundance off Central California",
        y_label = "Average Abundance catch per unit effort (ln(catch+1))",
        col_t   = "time (UTC)",
        col_y   = "mean_cpue (ln(catch+1))"
        #skip_lines
        #group_by  
        #std_err   
        , filter="species_group == \"YOY Pacific hake\""
    ),
    error = function(e) e
)
```


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "http://oceanview.pfeg.noaa.gov/erddap/tabledap/cciea_EI_FBC.csvp?time%2Cspecies_group%2Cmean_cpue%2CSeup%2CSelo&distinct()",
        title   = "YOY Sanddab (<i>Citharichthys spp.</i>) Abundance off Central California",
        y_label = "Average Abundance catch per unit effort (ln(catch+1))",
        col_t   = "time (UTC)",
        col_y   = "mean_cpue (ln(catch+1))"
        #skip_lines
        #group_by  
        #std_err   
        , filter="species_group == \"YOY sanddabs\""
    ),
    error = function(e) e
)
```
Source Data: Dr. John Field (NOAA; john.field@noaa.gov) from the SWFSC
Rockfish Recruitment and Ecosystem Assessment Survey
(https://swfsc.noaa.gov/textblock.aspx?Division=FED&ParentMenuId=54&id=20615).
Additional Calculations: Samples represent catch (individuals) per standard
15 minute trawl (CPUE). Data are log(CPUE+1) transformed; Geometric means
calculated on non-zero data.
