---
output:
html_document:
self_contained: false
lib_dir: "libs"
fig_height: 2
fig_width: 4
params:
element: "jellies"
---

```{r, echo=FALSE, message=F, warning=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F)
library(infographiq)
```

<base target="_parent">


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/forage_inverts/FED_Gelatinous_catch.csv",
        title   = "Gelatinous Catch",
        y_label = "Catch (number of species)",
        col_t   = "yr",
        col_y   = "catch"
        #skip_lines
        #group_by  
        #std_err   
        #filter
    ),
    error = function(e) e
)
```
Gelatinous species: Pyrosoma, Salp, Thetys Salp, Heteropd<br>
Jelly species: Fried Egg Jelly, Sea Nettle, Purple-striped Jelly, Moon Jelly.


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/forage_inverts/FED_Jellies_catch..csv",
        title   = "Jellies Catch",
        y_label = "Catch (number of species)",
        col_t   = "yr",
        col_y   = "catch"
        #skip_lines
        #group_by  
        #std_err   
        #filter
    ),
    error = function(e) e
)
```
The Fisheries Ecology Division (FED, https://swfsc.noaa.gov/GroundfishAnalysis/) of the Southwest Fisheries Science Center (SWFSC)  midwater trawl survey off central California. The data may be used and redistributed for free but is not intended
for legal use, since it may contain inaccuracies. Neither the data
Contributor, ERD, NOAA, nor the United States Government, nor any
of their employees or contractors, makes any warranty, express or
implied, including warranties of merchantability and fitness for a
particular purpose, or assumes any legal liability for the accuracy,
completeness, or usefulness, of this information. Fisheries Ecology Division/SWFSC/NOAA
