---
output: html_document
editor_options: 
  chunk_output_type: console
---
```{r setup, include=F}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
```

```{r}
source(here::here("scripts/oceano.R"))

nms       <- "cinms"
sites_csv <- here("data/sites.csv")

nms_ply <- get_nms_ply(nms)

if (F){
  st_centroid(nms_ply$geometry) %>% st_coordinates() %>% as_tibble() %>% 
    tail(1) %>% 
    mutate(id = !!nms) %>% 
    select(id, lon = X, lat = Y) %>% 
    write_csv(sites_csv)
}

site <- read_csv(here("data/sites.csv")) %>%
  filter(id == nms)

sst   <- info('jplMURSST41mday')
chl   <- info("nesdisVHNSQchlaMonthly")
scape <- info("noaa_aoml_4729_9ee6_ab54", url = "https://cwcgom.aoml.noaa.gov/erddap/")
```

## Maps {.tabset}

### Temperature

```{r}
# get most recent date
date_end <- get_dates(sst)[2]
```

Map of the most recent (`r format(date_end,"%Y-%m-%d")`) sea-surface temperature around the site. Data source: PFEG CoastWatch via ERDDAP.

```{r}
leaflet(
  nms_ply,
  options = leafletOptions(
    crs = leafletCRS(crsClass = "L.CRS.EPSG4326"))) %>%
  # basemap from GBIF in 4326
  addTiles("//tile.gbif.org/4326/omt/{z}/{x}/{y}@1x.png?style=gbif-geyser") %>%
  # sst
  addWMSTiles(
    baseUrl = 'https://coastwatch.pfeg.noaa.gov/erddap/wms/jplMURSST41mday/request?',
    layers = "jplMURSST41mday:sst",
    options = WMSTileOptions(
      version = "1.3.0", format = "image/png", transparent = T, opacity = 0.7,
      time = format(date_end,"%Y-%m-%dT00:00:00Z")))  %>%
  addPolygons() %>% 
  addMarkers(lng = ~lon, lat = ~lat, label = ~id, data=site) %>%
  addMouseCoordinates() %>%
  addLegend(
    position="bottomright",
    title = paste0("SST (°C)<br>", format(date_end,"%Y-%m-%d")),
    colorNumeric("Spectral", c(0,32), reverse=T), seq(0,32))
```

### Chlorophyll

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# get most recent date
d_2 <- get_dates(chl)[2]
```

Map of the most recent (`r format(d_2, "%Y-%m-%d")`) Chlorophyll-a around the site. Data Source: PFEG CoastWatch via ERDDAP.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
leaflet(
  nms_ply,
  options = leafletOptions(
    crs = leafletCRS(crsClass = "L.CRS.EPSG4326"))) %>%
  # basemap from GBIF in 4326
  addTiles("//tile.gbif.org/4326/omt/{z}/{x}/{y}@1x.png?style=gbif-geyser") %>%
  # sst
  addWMSTiles(
    baseUrl = 'https://coastwatch.pfeg.noaa.gov/erddap/wms/nesdisVHNSQchlaMonthly/request?',
    layers = "nesdisVHNSQchlaMonthly:chlor_a",
    options = WMSTileOptions(
      version = "1.3.0", format = "image/png", transparent = T, opacity = 0.7,
      time = format(d_2,"%Y-%m-%dT00:00:00Z")))  %>%
  addPolygons() %>% 
  addMarkers(lng = ~lon, lat = ~lat, label = ~id, data=site) %>%
  addMouseCoordinates() %>%
  addLegend(
    position="bottomright",
    title = paste0("CHL (mg m^-3)<br>", format(d_2,"%Y-%m-%d")),
    colorNumeric("Spectral", c(0,4), reverse=T), seq(0,4))
```

### Seascape

```{r, echo=FALSE, message=FALSE, warning=FALSE}
# get most recent date
d_2 <- get_dates(scape)[2]
```

Map of the most recent (`r format(d_2, "%Y-%m-%d")`) seascapes around the site. Data Source: AOML CWCGOM via ERDDAP.

```{r, echo=FALSE, message=FALSE, warning=FALSE}
leaflet(
  nms_ply,
  options = leafletOptions(
    crs = leafletCRS(crsClass = "L.CRS.EPSG4326"))) %>%
  # basemap from GBIF in 4326
  addTiles("//tile.gbif.org/4326/omt/{z}/{x}/{y}@1x.png?style=gbif-geyser") %>%
  # sst
  addWMSTiles(
    baseUrl = 'https://cwcgom.aoml.noaa.gov/erddap/wms/noaa_aoml_4729_9ee6_ab54/request?',
    layers = "noaa_aoml_4729_9ee6_ab54:CLASS",
    options = WMSTileOptions(
      version = "1.3.0", format = "image/png", transparent = T, opacity = 0.7,
      time = format(d_2,"%Y-%m-%dT00:00:00Z")))  %>%
  addPolygons() %>% 
  addMarkers(lng = ~lon, lat = ~lat, label = ~id, data=site) %>%
  addMouseCoordinates() %>%
  addLegend(
    position="bottomright",
    title = paste0("CLASS<br>", format(d_2,"%Y-%m-%d")),
    colorNumeric("Spectral", c(1,33), reverse=T), seq(1,33))
```

Read more about seascapes [here](http://www.marinebon.org/seascapes.html). 

## Timeseries {.tabset}

### Temperature

```{r, echo=FALSE, message=FALSE, warning=FALSE}
csv <- here(glue("data/oceano/sst_{nms}.csv"))
d   <- get_timeseries(sst, lon=site$lon, lat=site$lat, csv=csv, field="sst")
plot_timeseries(d, title="SST", color="red")
```

Download data: [`r basename(csv)`](https://raw.githubusercontent.com/marinebon/`r nms`/master/data/oceano/`r basename(csv)`)

### Chlorophyll

```{r, echo=FALSE, message=FALSE, warning=FALSE}
csv <- here(glue("data/oceano/chl_{nms}.csv"))
d_2   <- get_timeseries(chl, lon=site$lon, lat=site$lat, csv=csv, field="chlor_a")
plot_timeseries(d_2, title="CHL", color="green")
```

Download data: [`r basename(csv)`](https://raw.githubusercontent.com/marinebon/`r nms`/master/data/oceano/`r basename(csv))