---
output:
html_document:
self_contained: false
lib_dir: "libs"
fig_height: 2
fig_width: 4
params:
element: "pinnipeds"
---

```{r, echo=FALSE, message=F, warning=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F)
library(infographiq)
```

<base target="_parent">

Reduced amount of key forage contributed to low reproduction and high stranding rates for California sea lions and some seabirds. NOAA Fisheries declared a California Sea Lion Unusual Mortality Event in California due to the high numbers of strandings throughout the state.


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "http://oceanview.pfeg.noaa.gov/erddap/tabledap/cciea_MM_pup_count.csvp?time%2Clive_pup_count",
        title   = "Sea lion pup count San Miguel Isl.",
        y_label = "Average live pup count (number of species)",
        col_t   = "time (UTC)",
        col_y   = "live_pup_count (count)"
        #skip_lines
        #group_by  
        #std_err   
        #filter
    ),
    error = function(e) e
)
```


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "http://oceanview.pfeg.noaa.gov/erddap/tabledap/cciea_MM_pup_count.csvp?time%2Cmean_weight",
        title   = "Female sea lion pup weight index",
        y_label = "Mean pup weight (kg)",
        col_t   = "time (UTC)",
        col_y   = "mean_weight (kg)"
        #skip_lines
        #group_by  
        #std_err   
        #filter
    ),
    error = function(e) e
)
```


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "http://oceanview.pfeg.noaa.gov/erddap/tabledap/cciea_MM_pup_count.csvp?time%2Cmean_growth_rate",
        title   = "Female sea lion pup growth rate",
        y_label = "Mean growth rate (kg/day)",
        col_t   = "time (UTC)",
        col_y   = "mean_growth_rate (kg/day)"
        #skip_lines
        #group_by  
        #std_err   
        #filter
    ),
    error = function(e) e
)
```
California sea lion pups are counted at San Miguel Island, California. Live
pups are counted at the end of July each year, after all pups have been born.
Pups are weighed in September or October each year and weights are adjusted
using a mixed effects model to a 1 October weighing date. Growth rates are
predicted from a longitudinal sample of uniquely marked pups that are
captured in October and again the following February. Growth rates are
modeled using a mixed effects model and standard errors are estimated using
bootstrap. NOAA AFSC/MML http://www.noaa.gov/iea/Assets/iea/california/Report/pdf/10.%20Marine%20Mammals_2013.pdf
