---
output:
html_document:
self_contained: false
lib_dir: "libs"
fig_height: 2
fig_width: 4
params:
element: "salmon"
---

```{r, echo=FALSE, message=F, warning=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F)
library(infographiq)
```

<base target="_parent">


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/fish/CCIEA_Chinook_salmon_CC.csv",
        title   = "Chinook Salmon (<i>Oncorhynchus tshawytscha</i> Abundance off California",
        y_label = "Abundance anomaly (observed mean/standard deviation)",
        col_t   = "yr",
        col_y   = "abundance"
        #skip_lines
        #group_by  
        #std_err   
        #filter
    ),
    error = function(e) e
)
```
Calculations:  Abundance indices are calculated as longterm anomalies observed mean/standard deviation) of annual escapement by natural origin Fall Run Chinook to the Klamath and Trinity River systems. Data series for multiple subpopulations were standardized by subtracting the series mean and dividing by the series standard deviation. If a consolidated index for the stock was needed we computed an annual weighted average of the standardized series, with weights proportional to the average abundance for each subpopulation. NOAA NWFSC/SWFSC


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "http://oceanview.pfeg.noaa.gov/erddap/tabledap/cciea_SM_CA_CO_ABND.csvp?time%2Cpopulation%2Cabundance&time%3E=1987-01-01&time%3C=2015-01-01T00%3A00%3A00Z&population=%22CaCoastal%22",
        title   = "Coho Salmon (<i>Oncorhynchus kisutch</i> Abundance off California",
        y_label = "Abundance anomaly (observed mean/standard deviation)",
        col_t   = "time (UTC)",
        col_y   = "abundance"
        #skip_lines
        #group_by  
        #std_err   
        #filter
    ),
    error = function(e) e
)
```
NOAA NWFSC/SWFSC. The data may be used and redistributed for free but is not intended
for legal use, since it may contain inaccuracies. Neither the data
Contributor, ERD, NOAA, nor the United States Government, nor any
of their employees or contractors, makes any warranty, express or
implied, including warranties of merchantability and fitness for a
particular purpose, or assumes any legal liability for the accuracy,
completeness, or usefulness, of this information.
