---
output:
html_document:
self_contained: false
lib_dir: "libs"
fig_height: 2
fig_width: 4
params:
element: "SST"
---

```{r, echo=FALSE, message=F, warning=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F)
library(infographiq)
```

<base target="_parent">
Sea surface temperature data from satellite observations over the Monterey Bay National Marine Sanctuary (MBNMS). Data are processed by the Group for High Resolution Sea Surface Temperature (GHRSST) on a 0.25 degree (~ 27 km) grid.
<p></p>
<p>These graphs illustrate the 1982-1983 and 1997-1998 El Ni&ntilde;o events, and the 2015 event called "the Blob", a large mass of warm water in the Pacific Ocean off the coast of North America. First detected in late 2013, it continued to spread throughout 2014 and 2015. Local sea surface temperature in the MBNMS rose to a high of 17.93 degrees C. Based on long-term monitoring, it had very extensive impacts in MBNMS, and led to record high changes in many components: predator diversity, plankton blooms, and management actions were needed.</p>


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/MBNMS_GHRSST.csv",
        title   = "Mean Sea Surface Temperature from Satellite",
        y_label = "Deg C",
        col_t   = "Date",
        col_y   = "Mean SST"
        #skip_lines
        #group_by  
        #std_err   
        #filter
    ),
    error = function(e) e
)
```


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/MBNMS_GHRSST.csv",
        title   = "Sea Surface Temperature Anomaly from Satellite",
        y_label = "Deg C",
        col_t   = "Date",
        col_y   = "Anomaly"
        #skip_lines
        #group_by  
        #std_err   
        #filter
    ),
    error = function(e) e
)
```


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/MBNMS_MOD_CHL.csv",
        title   = "Mean CHL",
        y_label = "_",
        col_t   = "Date",
        col_y   = "Mean SST"
        #skip_lines
        #group_by  
        #std_err   
        #filter
    ),
    error = function(e) e
)
```


```{r out.width='100%'}
tryCatch(
    plot_dygraph_timeseries(
        csv_tv  = "https://raw.githubusercontent.com/marinebon/info-mb/master/prep/data/MBNMS_MOD_CHL.csv",
        title   = "CHL Anomaly",
        y_label = "_",
        col_t   = "Date",
        col_y   = "Anomaly"
        #skip_lines
        #group_by  
        #std_err   
        #filter
    ),
    error = function(e) e
)
```
The Group for High Resolution Sea Surface Temperature (GHRSST) is an open international science group that promotes the application of satellites for monitoring sea surface temperature (SST). The GHRSST Project Office is co-funded by the European Space Agency, the National Centre for Earth Observation, and the universities of Leicester and Reading. https://www.ghrsst.org
