---
output:
   html_document:
      self_contained: false
      keep_md: false
editor_options: 
  chunk_output_type: console
---

```{r, include=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F, error=F, eval = T)
library(magrittr)
library(infographiqR) # remotes::install_github("marinebon/infographiqR") 
library(onmsR) # remotes::install_github("noaa-onms/onmsR")

# The following is used by the plot_intertidal_nms function called later
#dir_gdrive <- "G:/Shared drives/NMS/data"
 dir_gdrive <- "/Volumes/GoogleDrive/Shared drives/NMS/data"
dir_pfx     <- file.path(dir_gdrive, "github_info-intertidal_data")
d_csv       <- file.path(dir_pfx, "sanctuary_species_percentcover.csv")
nms_rgns_csv    <- file.path(dir_pfx, "MARINe_graphs.xlsx - sites in regions.csv")
nms_rgns1 <- readr::read_csv(nms_rgns_csv) %>% 
  tidyr::fill(nms) %>% 
  dplyr::group_by(nms) %>% 
  tidyr::fill(region) %>% 
  dplyr::mutate(
    rgn = region) # View(nms_rgns)
```

`r infographiqR::get_modal_info()`

## {.tabset}

### Map of Sites

```{r map_nms_sites}
onmsR::map_nms_sites("cinms", dir_gdrive)
```
`r onmsR::md_caption("Interactive map of field sites across the Channel Islands")`

`r onmsR::md_caption("Interactive map of field sites across the Channel Islands", get_details = T)`
### Golden Rockweed (_Silvetia compressa_) {.active}

`r onmsR::get_figure_info("Golden rockweed")`

```{r}
onmsR::plot_intertidal_nms(d_csv, "CINMS", "SILCOM", "Golden Rockweed", nms_rgns1)
# TODO: LATER consider alternate ways
# p <- plot_intertidal_nms(d_csv, "CINMS", "SILCOM", "Golden Rockweed", download="img/Golden_rockweed.png")
```
`r onmsR::md_caption("Golden Rockweed")`

`r onmsR::md_caption("Golden Rockweed", get_details = T, fig_in_report = F)`

### Olive Rockweed (_Hesperophycus californicus_)
`r onmsR::get_figure_info("Olive rockweed")`
```{r}
onmsR::plot_intertidal_nms(d_csv, "CINMS", "HESCAL", "Olive Rockweed", nms_rgns1)
```
`r onmsR::md_caption("Olive Rockweed")`

`r onmsR::md_caption("Olive Rockweed", get_details = T, fig_in_report = F)`

### Turfweed (_Endocladia muricata_)
`r onmsR::get_figure_info("Turfweed")`
```{r}
# TODO: inspect Surfgrass in CINMS; n=1100; Error in seq.int(0, 1, length.out = n)
#plot_intertidal_nms(d_csv, "CINMS", "PHYOVR", "Surfgrass"):

onmsR::plot_intertidal_nms(d_csv, "CINMS", "ENDMUR", "Turfweed", nms_rgns1)
```
`r onmsR::md_caption("Turfweed")`

`r onmsR::md_caption("Turfweed", get_details = T, fig_in_report = F)`








