---
output:
   html_document:
      self_contained: false
      keep_md: false
editor_options: 
  chunk_output_type: console
---

```{r, include=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F, error=F, eval = T)
source(here::here("../cinms/scripts/rocky.R"))
source(here::here("scripts/utility.R"))
```

`r get_modal_info()`

## {.tabset}

### Map of Sites

```{r}
map_nms_sites("cinms")
```
`r render_caption("Interactive map of field sites across the Channel Islands")`

### Golden Rockweed (_Silvetia compressa_) {.active}

`r get_figure_info("Golden rockweed")`

```{r}
plot_intertidal_nms(d_csv, "CINMS", "SILCOM", "Golden Rockweed")
# TODO: LATER consider alternate ways
# p <- plot_intertidal_nms(d_csv, "CINMS", "SILCOM", "Golden Rockweed", download="img/Golden_rockweed.png")
```
`r render_caption("Golden Rockweed")`

### Olive Rockweed (_Hesperophycus californicus_)
`r get_figure_info("Olive rockweed")`
```{r}
plot_intertidal_nms(d_csv, "CINMS", "HESCAL", "Olive Rockweed")
```
`r render_caption("Olive Rockweed")`

### Turfweed (_Endocladia muricata_)
`r get_figure_info("Turfweed")`
```{r}
# TODO: inspect Surfgrass in CINMS; n=1100; Error in seq.int(0, 1, length.out = n)
#plot_intertidal_nms(d_csv, "CINMS", "PHYOVR", "Surfgrass"):

plot_intertidal_nms(d_csv, "CINMS", "ENDMUR", "Turfweed")
```
`r render_caption("Turfweed")`








