
```{r setup, include=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F, error=F)
library(magrittr)
library(nms4r)

# The following is used by the plot_intertidal_nms function called later
dir_gdrive <- "/Volumes/GoogleDrive/Shared drives/NMS/data"
dir_pfx     <- file.path(dir_gdrive, "github_info-intertidal_data")
d_csv       <- file.path(dir_pfx, "sanctuary_species_percentcover.csv")
nms_rgns_csv    <- file.path(dir_pfx, "MARINe_graphs.xlsx - sites in regions.csv")
nms_rgns1 <- readr::read_csv(nms_rgns_csv) %>% 
  tidyr::fill(nms) %>% 
  dplyr::group_by(nms) %>% 
  tidyr::fill(region) %>% 
  dplyr::mutate(
    rgn = region) # View(nms_rgns)
```

`r nms4r::get_modal_info()`

## {.tabset}

### Map of Sites

```{r map sites}
nms4r::map_nms_sites("cinms")
```
`r nms4r::md_caption("Interactive map of field sites across the Channel Islands")`

`r nms4r::md_caption("Interactive map of field sites across the Channel Islands", get_details = T)`
### Acorn barnacles (all plots)
`r nms4r::get_figure_info("Acorn barnacles (all plots)")`
```{r Acorn Barnacles all}
nms4r::plot_intertidal_nms(d_csv, "CINMS", "CHTBAL", "Acorn Barnacles", nms_rgns1)
```
`r nms4r::md_caption("Acorn barnacles_all")`

`r nms4r::md_caption("Acorn barnacles_all", get_details = T, fig_in_report = F)`

### Acorn barnacles (barnacle plots only)
`r nms4r::get_figure_info("Acorn barnacles (barnacle plots only)")`
```{r Acorn barnacles}
 nms4r::plot_intertidal_nms(d_csv, "CINMS", "CHTBAL", "Acorn Barnacles",  nms_rgns1, c("balanus", "chthamalus_balanus"))
```
`r nms4r::md_caption("Acorn barnacles")`

`r nms4r::md_caption("Acorn barnacles", get_details = T, fig_in_report = F)`
### Gooseneck barnacles (all plots)
`r nms4r::get_figure_info("Gooseneck barnacles (all plots)")`
```{r Goose Barnacle}
nms4r::plot_intertidal_nms(d_csv, "CINMS", "POLPOL", "Goose Barnacle", nms_rgns1)
```
`r nms4r::md_caption("Gooseneck barnacles")`

`r nms4r::md_caption("Gooseneck barnacles", get_details = T, fig_in_report = F)`
### Pink barnacles (all plots)
`r nms4r::get_figure_info("Pink barnacles (all plots)")`
```{r Pink Barnacle}
nms4r::plot_intertidal_nms(d_csv, "CINMS", "TETRUB", "Pink Barnacle", nms_rgns1)
```
`r nms4r::md_caption("Pink barnacles")`

`r nms4r::md_caption("Pink barnacles", get_details = T, fig_in_report = F)`
