
```{r, include=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F, error=F)
source(here::here("../cinms/scripts/rocky.R"))
source(here::here("scripts/utility.R"))
# Error in sp_target %in% spp_targets : object 'sp_target' not found
```

`r get_modal_info()`

## {.tabset}

### Map of Sites

```{r}
map_nms_sites("cinms")
```
`r render_caption("Interactive map of field sites across the Channel Islands")`

### Acorn barnacles (all plots)
`r get_figure_info("Acorn barnacles (all plots)")`
```{r}
plot_intertidal_nms(d_csv, "CINMS", "CHTBAL", "Acorn Barnacles")
```
`r render_caption("Acorn barnacles_all")`


### Acorn barnacles (barnacle plots only)
`r get_figure_info("Acorn barnacles (barnacle plots only)")`
```{r}
plot_intertidal_nms(d_csv, "CINMS", "CHTBAL", "Acorn Barnacles", c("balanus", "chthamalus_balanus"))
```
`r render_caption("Acorn barnacles")`

### Gooseneck barnacles (all plots)
`r get_figure_info("Gooseneck barnacles (all plots)")`
```{r}
plot_intertidal_nms(d_csv, "CINMS", "POLPOL", "Goose Barnacle")
```
`r render_caption("Gooseneck barnacles")`

### Pink barnacles (all plots)
`r get_figure_info("Pink barnacles (all plots)")`
```{r}
plot_intertidal_nms(d_csv, "CINMS", "TETRUB", "Pink Barnacle")
```
`r render_caption("Pink barnacles")`
