```{r, include=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F, error=F)
source(here::here("scripts/utility.R"))
```

```{r modal_info}
get_modal_info()
```

## {.tabset}

### Map of eelgrass beds

```{r, eval=F}
figure_name = "Figure App.E.10.22."
figure_location = "../img/cinms_cr/App.E.10.22.jpg"

# `r monitoring_info(figure_name)`
# 
# ![`r md_caption(figure_name)`](`r figure_location`)
# 
# `r md_caption(figure_name, get_details=T)`
```

`r render_figure("Figure App.E.10.22.", "../img/cinms_cr/App.E.10.22.jpg")`

### Eelgrass extent Anacapa Island
```{r}
figure_name = "Figure App.E.10.24."
figure_location = "../img/cinms_cr/App.E.10.24.jpg"
```

`r get_figure_info(figure_name)`

![`r md_caption(figure_name)`](`r figure_location`)

`r md_caption(figure_name, get_details=T)`

### Eelgrass extent Santa Cruz Island
```{r}
figure_name = "Figure App.E.10.25."
figure_location = "../img/cinms_cr/App.E.10.25.jpg"
```

`r get_figure_info(figure_name)`

![`r md_caption(figure_name)`](`r figure_location`)

`r md_caption(figure_name, get_details=T)`

### Eelgrass cover Frenchy's Cove
```{r}
figure_name = "Figure S.Hab.10.3."
figure_location = "../img/cinms_cr/S.Hab.10.3.jpg"
```

`r get_figure_info(figure_name)`

![`r md_caption(figure_name)`](`r figure_location`)

`r md_caption(figure_name, get_details=T)`


