---
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F, error=F)
library(glue)
library(nms4r)
```

`r nms4r::get_modal_info()`

## {.tabset}

### Map of Regions

```{r calcofi map, fig.cap=nms4r::md_caption("Figure App.F.12.17.new")}
nms4r::calcofi_map()
```

### Larval fish, cool-water species {.active}

##### CINMS Region

```{r calcofi plot 1}
grp   <- "Cool-water associated ichthyoplankton"
rgn   <- "CINMS"

title <- glue::glue("{grp} - {rgn} Region")
csv   <- glue::glue("https://raw.githubusercontent.com/marinebon/calcofi-analysis/master/data/{grp}_{rgn}.csv")

nms4r::calcofi_plot(csv = csv, title = title)
```

##### SoCal Shelf Region

```{r calcofi plot 2}
grp   <- "Cool-water associated ichthyoplankton"
rgn   <- "SoCal Shelf"

title <- glue::glue("{grp} - {rgn} Region")
csv   <- glue::glue("https://raw.githubusercontent.com/marinebon/calcofi-analysis/master/data/{grp}_{rgn}.csv")

#download.file(csv, "_tmp.csv")
nms4r::calcofi_plot(csv = csv, title = title)
```

`r nms4r::md_caption("Figure App.F.15.5")`

### Larval fish, warm-water species

##### CINMS Region

```{r calcofi plot 3}
grp   <- "Warm-water associated ichthyoplankton"
rgn   <- "CINMS"

title <- glue::glue("{grp} - {rgn} Region")
csv   <- glue::glue("https://raw.githubusercontent.com/marinebon/calcofi-analysis/master/data/{grp}_{rgn}.csv")

nms4r::calcofi_plot(csv = csv, title = title)
```

##### SoCal Shelf Region

```{r calcofi plot 4}
grp   <- "Warm-water associated ichthyoplankton"
rgn   <- "SoCal Shelf"

title <- glue::glue("{grp} - {rgn} Region")
csv   <- glue::glue("https://raw.githubusercontent.com/marinebon/calcofi-analysis/master/data/{grp}_{rgn}.csv")

nms4r::calcofi_plot(csv = csv, title = title)
```

####

`r nms4r::md_caption("Figure App.F.15.5")`

### Larval fish - Mean Species Richness

#### CINMS Region

`r nms4r::render_figure("Figure App.F.15.6.a-b.", "../img/cinms_cr/App.F.15.6.a.CalCOFI_diversity_richness-cinms.jpg")`

#### SoCal Shelf Region

`r nms4r::render_figure("Figure App.F.15.6.a-b.", "../img/cinms_cr/App.F.15.6.b.CalCOFI_diversity_richness-socal.jpg")`

### Larval fish - Mean Simpson Diversity

#### CINMS Region

`r nms4r::render_figure("Figure App.F.15.6.c-d.", "../img/cinms_cr/App.F.15.6.c.CalCOFI_diversity_diversity-cinms.jpg")`

#### SoCal Shelf Region

`r nms4r::render_figure("Figure App.F.15.6.c-d.", "../img/cinms_cr/App.F.15.6.d.CalCOFI_diversity_diversity-socal.jpg")`

