
```{r, include=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F, error=F)
library(glue)
library(infographiqR) # remotes::install_github("marinebon/infographiqR") 
library(onmsR) # remotes::install_github("noaa-onms/onmsR")
```

```{r modal_info}
infographiqR::get_modal_info(info_modal_links_csv = "https://docs.google.com/spreadsheets/d/1yEuI7BT9fJEcGAFNPM0mCq16nFsbn0b-bNirYPU5W8c/gviz/tq?tqx=out:csv&sheet=info_modal_links")
```

## {.tabset}

### Map of Regions

```{r, fig.cap=infographiqR::md_caption("Figure App.F.12.17.")}
onmsR::calcofi_map()
```

### Anchovies {.active}

#### CINMS Region

```{r}
infographiqR::get_figure_info("Figure App.F.12.19.hake")
grp   <- "Anchovy"
rgn   <- "CINMS"

title <- glue::glue("{grp} - {rgn} Region")
csv   <- glue::glue("https://raw.githubusercontent.com/marinebon/calcofi-analysis/master/data/{grp}_{rgn}.csv")

onmsR::calcofi_plot(csv = csv, title = title)
```

`r infographiqR::md_caption("Figure App.F.12.19.anchovy")`

`r infographiqR::md_caption("Figure App.F.12.19.anchovy", get_details = T)`
#### SoCal Shelf Region

```{r}
infographiqR::get_figure_info("Figure App.F.12.19.hake")

grp   <- "Anchovy"
rgn   <- "SoCal Shelf"

title <- glue::glue("{grp} - {rgn} Region")
csv   <- glue::glue("https://raw.githubusercontent.com/marinebon/calcofi-analysis/master/data/{grp}_{rgn}.csv")

#download.file(csv, "_tmp.csv")
onmsR::calcofi_plot(csv = csv, title = title)
```
`r infographiqR::md_caption("Figure App.F.12.19.anchovy_SoCal")`

`r infographiqR::md_caption("Figure App.F.12.19.anchovy_SoCal", get_details = T)`
### Hake

#### CINMS Region

`r infographiqR::render_figure("Figure App.F.12.19.hake", "../img/cinms_cr/App.F.12.19hake.CalCOFI_Med_ichthy.jpg")`

#### SoCal Shelf Region

`r infographiqR::render_figure("Figure App.F.12.19.hake", "../img/cinms_cr/App.F.12.19hake.CalCOFI_Med_ichthy.jpg")`

### Myctophids

#### CINMS Region

```{r}
infographiqR::get_figure_info("Figure App.F.12.19.hake")

grp   <- "Myctophids"
rgn   <- "CINMS"

title <- glue::glue("{grp} - {rgn} Region")
csv   <- glue::glue("https://raw.githubusercontent.com/marinebon/calcofi-analysis/master/data/{grp}_{rgn}.csv")

onmsR::calcofi_plot(csv = csv, title = title)
```

#### SoCal Shelf Region

`r infographiqR::get_figure_info("Figure App.F.12.19.myctophids")`

```{r}
grp   <- "Myctophids"
rgn   <- "SoCal Shelf"

title <- glue::glue("{grp} - {rgn} Region")
csv   <- glue::glue("https://raw.githubusercontent.com/marinebon/calcofi-analysis/master/data/{grp}_{rgn}.csv")

onmsR::calcofi_plot(csv = csv, title = title)
```

`r infographiqR::md_caption("Figure App.F.12.19.myctophids")`

`r infographiqR::md_caption("Figure App.F.12.19.myctophids", get_details = T)`

### Rockfish

#### CINMS Region

`r infographiqR::get_figure_info("Figure App.F.12.19.rockfish")`

```{r}
grp   <- "Rockfish"
rgn   <- "CINMS"

title <- glue::glue("{grp} - {rgn} Region")
csv   <- glue::glue("https://raw.githubusercontent.com/marinebon/calcofi-analysis/master/data/{grp}_{rgn}.csv")

onmsR::calcofi_plot(csv = csv, title = title)
```

#### SoCal Shelf Region

`r infographiqR::get_figure_info("Figure App.F.12.19.rockfish")`

```{r}
grp   <- "Rockfish"
rgn   <- "SoCal Shelf"

title <- glue::glue("{grp} - {rgn} Region")
csv   <- glue::glue("https://raw.githubusercontent.com/marinebon/calcofi-analysis/master/data/{grp}_{rgn}.csv")

onmsR::calcofi_plot(csv = csv, title = title)
```

`r infographiqR::md_caption("Figure App.F.12.19.rockfish")`

`r infographiqR::md_caption("Figure App.F.12.19.rockfish", get_details = T)`

### Sanddab

#### CINMS Region

```{r}
infographiqR::get_figure_info("Figure App.F.12.19.hake")

grp   <- "Sanddab"
rgn   <- "CINMS"

title <- glue::glue("{grp} - {rgn} Region")
csv   <- glue::glue("https://raw.githubusercontent.com/marinebon/calcofi-analysis/master/data/{grp}_{rgn}.csv")

onmsR::calcofi_plot(csv = csv, title = title)
```

#### SoCal Shelf Region

`r infographiqR::get_figure_info("Figure App.F.12.19.sanddab")`

```{r}
grp   <- "Sanddab"
rgn   <- "SoCal Shelf"

title <- glue::glue("{grp} - {rgn} Region")
csv   <- glue::glue("https://raw.githubusercontent.com/marinebon/calcofi-analysis/master/data/{grp}_{rgn}.csv")

onmsR::calcofi_plot(csv = csv, title = title)
```

`r infographiqR::md_caption("Figure App.F.12.19.sanddab")`

`r infographiqR::md_caption("Figure App.F.12.19.sanddab", get_details = T)`

### Sardines

#### CINMS Region

```{r}
infographiqR::get_figure_info("Figure App.F.12.19.hake")

grp   <- "Sardine"
rgn   <- "CINMS"

title <- glue::glue("{grp} - {rgn} Region")
csv   <- glue::glue("https://raw.githubusercontent.com/marinebon/calcofi-analysis/master/data/{grp}_{rgn}.csv")

onmsR::calcofi_plot(csv = csv, title = title)
```

#### SoCal Shelf Region

`r infographiqR::get_figure_info("Figure App.F.12.19.sardine")`

```{r}
grp   <- "Sardine"
rgn   <- "SoCal Shelf"

title <- glue::glue("{grp} - {rgn} Region")
csv   <- glue::glue("https://raw.githubusercontent.com/marinebon/calcofi-analysis/master/data/{grp}_{rgn}.csv")

onmsR::calcofi_plot(csv = csv, title = title)
```

`r infographiqR::md_caption("Figure App.F.12.19.sardine")`

`r infographiqR::md_caption("Figure App.F.12.19.sardine", get_details = T)`
