---
pagetitle: "Key climate & ocean drivers"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=F}
knitr::opts_chunk$set(echo = F, message = F, warning = F)
source(here::here("scripts/utility.R"))
```

```{r svg, child = '_key-climate-ocean.Rmd'}
```

`r get_modal_info()`

# {.tabset}

## Temperature {.tabset}
### Map: Satellite-based SST (CoastWatch)

```{r}
# get most recent date
date_end <- get_dates(sst)[2]

leaflet(
  nms_ply,
  options = leafletOptions(
    crs = leafletCRS(crsClass = "L.CRS.EPSG4326"))) %>%
  # basemap from GBIF in 4326
  addTiles("//tile.gbif.org/4326/omt/{z}/{x}/{y}@1x.png?style=gbif-geyser") %>%
  # sst
  addWMSTiles(
    baseUrl = 'https://coastwatch.pfeg.noaa.gov/erddap/wms/jplMURSST41mday/request?',
    layers = "jplMURSST41mday:sst",
    options = WMSTileOptions(
      version = "1.3.0", format = "image/png", transparent = T, opacity = 0.7,
      time = format(date_end,"%Y-%m-%dT00:00:00Z")))  %>%
  addPolygons() %>% 
  addMarkers(lng = ~lon, lat = ~lat, label = ~id, data=site) %>%
  addMouseCoordinates() %>%
  addLegend(
    position="bottomright",
    title = paste0("SST (°C)<br>", format(date_end,"%Y-%m-%d")),
    colorNumeric("Spectral", c(0,32), reverse=T), seq(0,32))
```

`r md_caption("Figure Ux.Ocean.SST.ERD.map.")`

`r md_caption("Figure Ux.Ocean.SST.ERD.map.", get_details = T)`



### Trend: Satellite-based SST (CoastWatch)

```{r}
csv  <- here(glue("data/oceano/sst_{nms}.csv"))
url  <- glue("https://github.com/marinebon/{nms}/raw/master/data/oceano/{basename(csv)}")
html <- a(basename(csv), href=url, target='_blank')

d   <- get_timeseries(sst, lon=site$lon, lat=site$lat, csv=csv, field="sst")
plot_timeseries(d, title="SST", color="red")
```

`r md_caption("Figure Ux.Ocean.SST.ERD.timeseries.")`

`r md_caption("Figure Ux.Ocean.SST.ERD.timeseries.", get_details = T)`

Download timeseries data for sanctuary: `r html`

### Trend: SST anomaly (SBC LTER)
### Trend: Temperature profile (PnB)

`r render_figure("Figure App.D.8.4.", "../img/cinms_cr/App.D.8.4.png")`

## Acidification {.tabset}
#### Aragonite saturation

`r render_figure("Figure App.E.10.29.", "../img/cinms_cr/App.E.10.29.jpg")`

## Harmful Algal Blooms {.tabset}

#### Trends: Domoic Acid Levels (2012-13)

`r render_figure("Figure App.D.7.1.", "../img/cinms_cr/App.D.7.1_DA levels in crustaceans and bivalves in 2012 and 2013_C. Culver CA Sea Grant copy.jpg")`

#### Map: Harmful Algal Bloom (2015)

`r render_figure("Figure App.D.7.3.", "../img/cinms_cr/App.D.7.3_2015 HAB_McCabe et al. 2016.jpg")`

## Chlorophyll {.tabset}

### Map: Satellite-based (CoastWatch)
```{r}
# get most recent date
d_2 <- get_dates(chl)[2]

leaflet(
  nms_ply,
  options = leafletOptions(
    crs = leafletCRS(crsClass = "L.CRS.EPSG4326"))) %>%
  # basemap from GBIF in 4326
  addTiles("//tile.gbif.org/4326/omt/{z}/{x}/{y}@1x.png?style=gbif-geyser") %>%
  # sst
  addWMSTiles(
    baseUrl = 'https://coastwatch.pfeg.noaa.gov/erddap/wms/nesdisVHNSQchlaMonthly/request?',
    layers = "nesdisVHNSQchlaMonthly:chlor_a",
    options = WMSTileOptions(
      version = "1.3.0", format = "image/png", transparent = T, opacity = 0.7,
      time = format(d_2,"%Y-%m-%dT00:00:00Z")))  %>%
  addPolygons() %>% 
  addMarkers(lng = ~lon, lat = ~lat, label = ~id, data=site) %>%
  addMouseCoordinates() %>%
  addLegend(
    position="bottomright",
    title = paste0("CHL (mg m^-3)<br>", format(d_2,"%Y-%m-%d")),
    colorNumeric("Spectral", c(0,4), reverse=T), seq(0,4))
```

`r md_caption("Figure Ux.Ocean.Chl.ERD.map.")`

`r md_caption("Figure Ux.Ocean.Chl.ERD.map.", get_details = T)`
### Trend: Satellite-based (CoastWatch)

```{r}
csv  <- here(glue("data/oceano/chl_{nms}.csv"))
url  <- glue("https://github.com/marinebon/{nms}/raw/master/data/oceano/{basename(csv)}")
html <- a(basename(csv), href=url, target='_blank')

d_2   <- get_timeseries(chl, lon=site$lon, lat=site$lat, csv=csv, field="chlor_a")
plot_timeseries(d_2, title="CHL", color="green")
```

`r md_caption("Figure Ux.Ocean.Chl.ERD.timeseries.")`

`r md_caption("Figure Ux.Ocean.Chl.ERD.timeseries.", get_details = T)`

Download timeseries data for sanctuary: `r html`


## Nutrients {.tabset}

### Trend: Nitrate profile (PnB)

`r render_figure("Figure App.D.6.5.", "../img/cinms_cr/App.D.6.5.png")`

### Trend: Phosphate profile (PnB)

`r render_figure("Figure App.D.6.6.", "../img/cinms_cr/App.D.6.6.png")`

### Trend: Nitrate anomaly

`r render_figure("Figure App.D.6.7.", "../img/cinms_cr/App.D.6.7_SST and nitrate anomalies 2001-2015_Reed et al._2016.jpg")`

## Basin Scale Indices
### Trend: ONI, PDO, NPGO

`r render_figure("Figure App.D.8.3.", "../img/cinms_cr/App.D.8.3.png")`

## Metrics under construction (coming soon)
### Seafloor Temperature

No data are available at this time, please check back soon!

### Upwelling Index

No data are available at this time, please check back soon!

### Wave Height & Direction

No data are available at this time, please check back soon!

### Sea Level Height

No data are available at this time, please check back soon!

### Air Temperature

No data are available at this time, please check back soon!

### pH

No data are available at this time, please check back soon!

### Dissolved Oxygen

No data are available at this time, please check back soon!

### Depth of Anoxic Layer

No data are available at this time, please check back soon!


