---
pagetitle: "Key climate & ocean drivers"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=F}
knitr::opts_chunk$set(
	echo = F,
	message = FALSE,
	warning = FALSE
)
```

```{r svg, child = '_key-climate-ocean.Rmd'}
```

`r nms4r::get_modal_info()`

# {.tabset}

## Temperature {.tabset}
### Map: Satellite-based SST 

```{r sst_map}
# get most recent date
date_end <- nms4r::get_dates(sst)[2]

leaflet(
  nms_ply,
  options = leafletOptions(
    crs = leafletCRS(crsClass = "L.CRS.EPSG4326"))) %>%
  # basemap from GBIF in 4326
  addTiles("//tile.gbif.org/4326/omt/{z}/{x}/{y}@1x.png?style=gbif-geyser") %>%
  # sst
  addWMSTiles(
    baseUrl = 'https://coastwatch.pfeg.noaa.gov/erddap/wms/jplMURSST41mday/request?',
    layers = "jplMURSST41mday:sst",
    options = WMSTileOptions(
      version = "1.3.0", format = "image/png", transparent = T, opacity = 0.7,
      time = format(date_end,"%Y-%m-%dT00:00:00Z")))  %>%
  addPolygons() %>%
  addMouseCoordinates() %>%
  leaflet::addLegend(
    position="bottomright",
    title = paste0("SST (째C)<br>", format(date_end,"%Y-%m-%d")),
    colorNumeric("Spectral", c(0,32), reverse=T), seq(0,32))
```

`r nms4r::md_caption("Figure Ux.Ocean.SST.ERD.map.")`

`r nms4r::md_caption("Figure Ux.Ocean.SST.ERD.map.", get_details = T)`

### Trend: Satellite-based SST 

```{r sst_time_series}
csv_SST <-here(glue("data/oceano/statistics_sst_{nms}.csv"))
url_SST  <- glue("https://github.com/marinebon/{nms}/raw/master/data/oceano/{basename(csv_SST)}")
html_SST <- a(basename(csv_SST), href=url_SST, target='_blank')
nms4r::plot_metric_timeseries(csv_SST, "sst")
```

`r nms4r::md_caption("Figure Ux.Ocean.SST.ERD.timeseries.")`

`r nms4r::md_caption("Figure Ux.Ocean.SST.ERD.timeseries.", get_details = T)`

Download timeseries data for sanctuary: `r html_SST`

### Trend: SST anomaly

```{r sst anomaly time series}
csv_SST <-here::here(glue::glue("data/oceano/sst_anomaly_{nms}.csv"))
url_SST  <- glue::glue("https://github.com/marinebon/{nms}/raw/master/data/oceano/{basename(csv_SST)}")
html_SST <- htmltools::a(basename(csv_SST), href=url_SST, target='_blank')

# We want to plot the SST anomaly data with values below zero colored differently
# than those above zero. The strategy here is to split the SST anomaly data (which 
# is 1 column of data) into 2 columns of data: values below zero and values above 
# zero. Each of those lines will be plotted separately as a different filled-in 
# color. We also need to interpolate some points. Every time the anomaly time 
# series data crosses the zero anomaly line (0 on the y axis), that "zero day" 
# needs to be inserted into the 2 columns of data. This is necessary to have a 
# figure that doesn't have gaps in the color fill.

# load in the SST anomaly data
# csv_SST <-here::here("data/oceano/sst_anomaly_cinms.csv")
SST_data<-read.csv(csv_SST, header = T, colClasses = c("Date", "numeric"))

# create an output data frame and initialize the row of the data frame to write
# on to 1
output_data<-data.frame(date= SST_data$date,below=NA,above=NA )
write_line <-1

# Let's go through every row of the anomaly data
for (i in 1:nrow(SST_data)){
  
  # first let's write the row of data to the output data frame, putting below 
  # zero and above zero values in different columns
  if (SST_data$sst_anomaly[i] <= 0){
    output_data[write_line,]<- c(as.character(SST_data$date[i]), 
                                 as.numeric(SST_data$sst_anomaly[i]), NA)
  }
  else {
    output_data[write_line,]<- c(as.character(SST_data$date[i]), NA, 
                                 as.numeric(SST_data$sst_anomaly[i]))
  }
  write_line <- write_line +1
  
  # Next, let's see if the anomaly value AFTER the current one changes sign.
  # If it does, we need to calculate the date at which the anomaly was zero and 
  # insert that "zero day" into the output file after the current anomaly value. 
  # We want to skip this whole procedure if we are at the last record of the file. 
  if ((i < nrow(SST_data)) && (sign(SST_data$sst_anomaly[i]) != 
                               sign(SST_data$sst_anomaly[i+1])) ){
    first_SST <- SST_data$sst_anomaly[i]
    second_SST <- SST_data$sst_anomaly[i+1]
    first_date <- SST_data$date[i]
    second_date <- SST_data$date[i+1]
    day_num <- as.numeric(second_date - first_date)
    daily_increment <- (second_SST - first_SST)/day_num
    days_more <- round(abs(first_SST/daily_increment),0)
    output_data[write_line, ] <- c(as.character(first_date + days_more), 0, 0)
    write_line <- write_line +1
  }
}

# create the data frame to be read by dygraphs and then produce the dygraph figure
history <- data.frame(date = as.Date(output_data$date, "%Y-%m-%d"), 
                      below = as.numeric(output_data$below), 
                      above = as.numeric(output_data$above))
history <- xts::xts(x = history[,-1], order.by = history$date)

dygraphs::dygraph(history, main = "Sea Surface Temperature Anomaly", xlab = "Date", ylab = "Sea Surface Temperature Anomaly (째C)") %>%
  dygraphs::dyOptions(fillGraph = TRUE, fillAlpha = 0.4) %>%
  dygraphs::dySeries("below", label = "째C Below Average", color = "Blue") %>% 
  dygraphs::dySeries("above", label = "째C Above Average", color = "Red") %>% 
  dygraphs::dyLegend(show = "auto", showZeroValues = FALSE) %>% 
  dyLimit(0, strokePattern = "solid", color = "black") %>% 
  dygraphs::dyRangeSelector(fillColor = " #FFFFFF", strokeColor = "#FFFFFF")
```

`r nms4r::md_caption("Figure Ux.Ocean.SST.Anomaly.timeseries.")`

`r nms4r::md_caption("Figure Ux.Ocean.SST.Anomaly.timeseries.", get_details = T)`

Download timeseries data for sanctuary: `r html_SST`

### Trend: Temperature profile (PnB)

`r nms4r::render_figure("Figure App.D.8.4.", "../img/cinms_cr/App.D.8.4.png")`

## Acidification {.tabset}
#### Aragonite saturation

`r nms4r::render_figure("Figure App.E.10.29.", "../img/cinms_cr/App.E.10.29.jpg")`

## Harmful Algal Blooms {.tabset}

#### Trends: Domoic Acid Levels (2012-13)

`r nms4r::render_figure("Figure App.D.7.1.", "../img/cinms_cr/App.D.7.1_DA levels in crustaceans and bivalves in 2012 and 2013_C. Culver CA Sea Grant copy.jpg")`

#### Map: Harmful Algal Bloom (2015)

`r nms4r::render_figure("Figure App.D.7.3.", "../img/cinms_cr/App.D.7.3_2015 HAB_McCabe et al. 2016.jpg")`

## Chlorophyll {.tabset}

### Map: Satellite-based (CoastWatch)
```{r chlorophyll_map}
# get most recent date
if ("try-error" %in% class(chl)){
  d_2 <- read_csv(here("data/oceano/avg-chl_cinms.csv")) %>% 
    arrange(date) %>% 
    tail(1) %>% 
    pull(date)
} else {
  d_2 <- nms4r::get_dates(chl)[2]
}

leaflet(
  nms_ply,
  options = leafletOptions(
    crs = leafletCRS(crsClass = "L.CRS.EPSG4326"))) %>%
  # basemap from GBIF in 4326
  addTiles("//tile.gbif.org/4326/omt/{z}/{x}/{y}@1x.png?style=gbif-geyser") %>%
  # sst
  addWMSTiles(
    baseUrl = 'https://coastwatch.pfeg.noaa.gov/erddap/wms/nesdisVHNSQchlaMonthly/request?',
    layers = "nesdisVHNSQchlaMonthly:chlor_a",
    options = WMSTileOptions(
      version = "1.3.0", format = "image/png", transparent = T, opacity = 0.7,
      time = format(d_2,"%Y-%m-%dT00:00:00Z")))  %>%
  addPolygons() %>%
  addMouseCoordinates() %>%
  leaflet::addLegend(
    position="bottomright",
    title = paste0("CHL (mg/m<sup>3</sup>)<br>", format(d_2,"%Y-%m-%d")),
    colorNumeric("Spectral", c(0,4), reverse=T), seq(0,4))
```

`r nms4r::md_caption("Figure Ux.Ocean.Chl.ERD.map.")`

`r nms4r::md_caption("Figure Ux.Ocean.Chl.ERD.map.", get_details = T)`
### Trend: Satellite-based (CoastWatch)

```{r chlorophyll_time_series}
csv_chl <-here(glue("data/oceano/statistics_chl_{nms}.csv"))
url_chl  <- glue("https://github.com/marinebon/{nms}/raw/master/data/oceano/{basename(csv_chl)}")
html_chl <- a(basename(csv_chl), href=url_chl, target='_blank')
nms4r::plot_metric_timeseries(csv_chl, "chl")
```

`r nms4r::md_caption("Figure Ux.Ocean.Chl.ERD.timeseries.")`

`r nms4r::md_caption("Figure Ux.Ocean.Chl.ERD.timeseries.", get_details = T)`

Download timeseries data for sanctuary: `r html_chl`

## Nutrients {.tabset}

### Trend: Nitrate profile (PnB)

`r nms4r::render_figure("Figure App.D.6.5.", "../img/cinms_cr/App.D.6.5.png")`

### Trend: Phosphate profile (PnB)

`r nms4r::render_figure("Figure App.D.6.6.", "../img/cinms_cr/App.D.6.6.png")`

### Trend: Nitrate anomaly

`r nms4r::render_figure("Figure App.D.6.7.", "../img/cinms_cr/App.D.6.7_SST and nitrate anomalies 2001-2015_Reed et al._2016.jpg")`

## Basin Scale Indices
### Trend: ONI, PDO, NPGO

`r nms4r::render_figure("Figure App.D.8.3.", "../img/cinms_cr/App.D.8.3.png")`

## Metrics under construction (coming soon)
### Seafloor Temperature

No data are available at this time, please check back soon!

### Upwelling Index

No data are available at this time, please check back soon!

### Wave Height & Direction

No data are available at this time, please check back soon!

### Sea Level Height

No data are available at this time, please check back soon!

### Air Temperature

No data are available at this time, please check back soon!

### pH

No data are available at this time, please check back soon!

### Dissolved Oxygen

No data are available at this time, please check back soon!

### Depth of Anoxic Layer

No data are available at this time, please check back soon!


