---
pagetitle: "Key climate & ocean drivers"
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=F}
knitr::opts_chunk$set(
	echo = F,
	message = FALSE,
	warning = FALSE
)
```

```{r svg, child = '_key-climate-ocean.Rmd'}
```

`r nms4r::get_modal_info()`

# {.tabset}

## Temperature {.tabset}
### Map: Satellite-based SST 

```{r sst_map}
# get most recent date
date_end <- nms4r::get_dates(sst)[2]

leaflet(
  nms_ply,
  options = leafletOptions(
    crs = leafletCRS(crsClass = "L.CRS.EPSG4326"))) %>%
  # basemap from GBIF in 4326
  addTiles("//tile.gbif.org/4326/omt/{z}/{x}/{y}@1x.png?style=gbif-geyser") %>%
  # sst
  addWMSTiles(
    baseUrl = 'https://coastwatch.pfeg.noaa.gov/erddap/wms/jplMURSST41mday/request?',
    layers = "jplMURSST41mday:sst",
    options = WMSTileOptions(
      version = "1.3.0", format = "image/png", transparent = T, opacity = 0.7,
      time = format(date_end,"%Y-%m-%dT00:00:00Z")))  %>%
  addPolygons() %>%
  addMouseCoordinates() %>%
  leaflet::addLegend(
    position="bottomright",
    title = paste0("SST (°C)<br>", format(date_end,"%Y-%m-%d")),
    colorNumeric("Spectral", c(0,32), reverse=T), seq(0,32))
```

`r nms4r::md_caption("Figure Ux.Ocean.SST.ERD.map.")`

`r nms4r::md_caption("Figure Ux.Ocean.SST.ERD.map.", get_details = T, fig_in_report = F)`

### Trend: Satellite-based SST 

```{r sst_time_series}
csv_SST <-here::here(glue::glue("data/oceano/statistics_sst_{nms}.csv"))
url_SST  <- glue::glue("https://github.com/marinebon/{nms}/raw/master/data/oceano/{basename(csv_SST)}")
html_SST <- htmltools::a(basename(csv_SST), href=url_SST, target='_blank')
nms4r::plot_metric_timeseries(csv_SST, "sst")
```

`r nms4r::md_caption("Figure Ux.Ocean.SST.ERD.timeseries.")`

`r nms4r::md_caption("Figure Ux.Ocean.SST.ERD.timeseries.", get_details = T, fig_in_report = F)`

Download timeseries data for sanctuary: `r html_SST`

### Trend: SST anomaly

```{r sst anomaly time series}
csv_SST <-here::here(glue::glue("data/oceano/sst_anomaly_{nms}.csv"))
url_SST  <- glue::glue("https://github.com/marinebon/{nms}/raw/master/data/oceano/{basename(csv_SST)}")
html_SST <- htmltools::a(basename(csv_SST), href=url_SST, target='_blank')
nms4r::plot_SST_anomaly(csv_SST)
```

`r nms4r::md_caption("Figure Ux.Ocean.SST.Anomaly.timeseries.")`

`r nms4r::md_caption("Figure Ux.Ocean.SST.Anomaly.timeseries.", get_details = T, fig_in_report = F)`

Download timeseries data for sanctuary: `r html_SST`

### Trend: Temperature profile (PnB)

`r nms4r::render_figure("Figure App.D.8.4.", "../img/cinms_cr/App.D.8.4.png")`

## Acidification {.tabset}
#### Aragonite saturation

`r nms4r::render_figure("Figure App.E.10.29.", "../img/cinms_cr/App.E.10.29.jpg")`

## Harmful Algal Blooms {.tabset}

#### Trends: Domoic Acid Levels (2012-13)

`r nms4r::render_figure("Figure App.D.7.1.", "../img/cinms_cr/App.D.7.1_DA levels in crustaceans and bivalves in 2012 and 2013_C. Culver CA Sea Grant copy.jpg")`

#### Map: Harmful Algal Bloom (2015)

`r nms4r::render_figure("Figure App.D.7.3.", "../img/cinms_cr/App.D.7.3_2015 HAB_McCabe et al. 2016.jpg")`

## Chlorophyll {.tabset}

### Map: Satellite-based (CoastWatch)
```{r chlorophyll_map}
# get most recent date
if ("try-error" %in% class(chl)){
  d_2 <- read_csv(here("data/oceano/avg-chl_cinms.csv")) %>% 
    arrange(date) %>% 
    tail(1) %>% 
    pull(date)
} else {
  d_2 <- nms4r::get_dates(chl)[2]
}

leaflet(
  nms_ply,
  options = leafletOptions(
    crs = leafletCRS(crsClass = "L.CRS.EPSG4326"))) %>%
  # basemap from GBIF in 4326
  addTiles("//tile.gbif.org/4326/omt/{z}/{x}/{y}@1x.png?style=gbif-geyser") %>%
  # sst
  addWMSTiles(
    baseUrl = 'https://coastwatch.pfeg.noaa.gov/erddap/wms/nesdisVHNSQchlaMonthly/request?',
    layers = "nesdisVHNSQchlaMonthly:chlor_a",
    options = WMSTileOptions(
      version = "1.3.0", format = "image/png", transparent = T, opacity = 0.7,
      time = format(d_2,"%Y-%m-%dT00:00:00Z")))  %>%
  addPolygons() %>%
  addMouseCoordinates() %>%
  leaflet::addLegend(
    position="bottomright",
    title = paste0("CHL (mg/m<sup>3</sup>)<br>", format(d_2,"%Y-%m-%d")),
    colorNumeric("Spectral", c(0,4), reverse=T), seq(0,4))
```

`r nms4r::md_caption("Figure Ux.Ocean.Chl.ERD.map.")`

`r nms4r::md_caption("Figure Ux.Ocean.Chl.ERD.map.", get_details = T, fig_in_report = F)`
### Trend: Satellite-based (CoastWatch)

```{r chlorophyll_time_series}
csv_chl <-here(glue("data/oceano/statistics_chl_{nms}.csv"))
url_chl  <- glue("https://github.com/marinebon/{nms}/raw/master/data/oceano/{basename(csv_chl)}")
html_chl <- a(basename(csv_chl), href=url_chl, target='_blank')
nms4r::plot_metric_timeseries(csv_chl, "chl")
```

`r nms4r::md_caption("Figure Ux.Ocean.Chl.ERD.timeseries.")`

`r nms4r::md_caption("Figure Ux.Ocean.Chl.ERD.timeseries.", get_details = T, fig_in_report = F)`

Download timeseries data for sanctuary: `r html_chl`

## Nutrients {.tabset}

### Trend: Nitrate profile (PnB)

`r nms4r::render_figure("Figure App.D.6.5.", "../img/cinms_cr/App.D.6.5.png")`

### Trend: Phosphate profile (PnB)

`r nms4r::render_figure("Figure App.D.6.6.", "../img/cinms_cr/App.D.6.6.png")`

### Trend: Nitrate anomaly

`r nms4r::render_figure("Figure App.D.6.7.", "../img/cinms_cr/App.D.6.7_SST and nitrate anomalies 2001-2015_Reed et al._2016.jpg")`

## Basin Scale Indices
### Trend: ONI, PDO, NPGO

`r nms4r::render_figure("Figure App.D.8.3.", "../img/cinms_cr/App.D.8.3.png")`

## Metrics under construction (coming soon)
### Seafloor Temperature

No data are available at this time, please check back soon!

### Upwelling Index

No data are available at this time, please check back soon!

### Wave Height & Direction

No data are available at this time, please check back soon!

### Sea Level Height

No data are available at this time, please check back soon!

### Air Temperature

No data are available at this time, please check back soon!

### pH

No data are available at this time, please check back soon!

### Dissolved Oxygen

No data are available at this time, please check back soon!

### Depth of Anoxic Layer

No data are available at this time, please check back soon!


