
```{r, include=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F, error=F)
library(magrittr)

# Let's pull the nms4r package from github, but only if it isn't already installed. We don't want to
# pull the package unnecessarily as github allows a max of 60 unauthenticated requests per hour.
ip = installed.packages()[,1]
if (all(ip!="nms4r")){
  library(devtools)
  devtools::install_github("marinebon/nms4r")
}

# The following is used by the plot_intertidal_nms function called later
dir_gdrive <- "/Volumes/GoogleDrive/Shared drives/NMS/data"
dir_pfx     <- file.path(dir_gdrive, "github_info-intertidal_data")
d_csv       <- file.path(dir_pfx, "sanctuary_species_percentcover.csv")
nms_rgns_csv    <- file.path(dir_pfx, "MARINe_graphs.xlsx - sites in regions.csv")
nms_rgns1 <- readr::read_csv(nms_rgns_csv) %>% 
  tidyr::fill(nms) %>% 
  dplyr::group_by(nms) %>% 
  tidyr::fill(region) %>% 
  dplyr::mutate(
    rgn = region) # View(nms_rgns)
```

`r nms4r::get_modal_info()`

## {.tabset}

### Map of Sites

```{r}
nms4r::map_nms_sites("cinms")
```

`r nms4r::md_caption("Interactive map of field sites across the Channel Islands")`

`r nms4r::md_caption("Interactive map of field sites across the Channel Islands", get_details = T)`

### California Mussels (_Mytilus californianus_){.active}
`r nms4r::get_figure_info("California Mussels")`

```{r}
nms4r::plot_intertidal_nms(d_csv, "CINMS", "MYTCAL", "California Mussels", nms_rgns1)
```
`r nms4r::md_caption("California Mussels")`

`r nms4r::md_caption("California Mussels", get_details = T)`

<!--
### California Mussels (_Mytilus californianus_), target = mytilus

```{r, eval =F}
#BB TODO: fix nms4r::plot_intertidal_nms() to accommodate target species
nms4r::plot_intertidal_nms(d_csv, "CINMS", "MYTCAL", "California Mussels [target = mytilus]", "mytilus", nms_rgns1)
```
-->
