---
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r, include=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F, error=F)
source(here::here("../cinms/scripts/rocky.R"))
source(here::here("../cinms/scripts/utility.R"))
```

```{r}
get_modal_info()
```

##  {.tabset} 

### MARINe: Map of Sites

```{r}
map_nms_sites("cinms")
```

`r md_caption("Figure Ux.Rocky.MARINe.map.")`

`r md_caption("Figure Ux.Rocky.MARINe.map.", get_details=T)`

### MARINe: Ochre Seastar (_Pisaster ochraceus_) {.active}

```{r}
plot_intertidal_nms(nms_spp_sscount_csv, "CINMS", "PISOCH", "Ochre Seastar", fld_val = "count", label_y = "Count (annual avg)")
```

`r md_caption("Figure Ux.Rocky.MARINe.Ochre-Stars.")`

`r md_caption("Figure Ux.Rocky.MARINe.Ochre-Stars.", get_details=T)`

### CHIS: Sanctuary

`r render_figure("Figure App.F.12.2.", "../img/cinms_cr/App.F.12.2.Pochraceus_abundance.jpg")`


### CHIS: Individual Islands

`r render_figure("Figure App.F.12.3.", "../img/cinms_cr/App.F.12.3.Pochraceus_size.jpg")`

