---
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r, include=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F, error=F)
source(here::here("../cinms/scripts/rocky.R"))
source(here::here("../cinms/scripts/utility.R"))
```

`r get_modal_info()`

##  {.tabset} 

### MARINe: Map of Sites

`r get_figure_info("Figure App.F.12.2.")`

```{r}
map_nms_sites("cinms")
```

`r render_caption("Figure Ux.Rocky.MARINe.map.")`

### MARINe: Ochre Seastar (_Pisaster ochraceus_) {.active}

`r get_figure_info("Figure App.F.12.2.")`

```{r}
plot_intertidal_nms(nms_spp_sscount_csv, "CINMS", "PISOCH", "Ochre Seastar", fld_val = "count", label_y = "Count (annual avg)")
```

`r render_caption("Figure Ux.Rocky.MARINe.Ochre-Stars.")`

### CHIS: Ochre Seastars arcoss the sanctuary

`r render_figure("Figure App.F.12.2.", "../img/cinms_cr/App.F.12.2.Pochraceus_abundance.jpg")`

### CHIS: Ochre Seastars at Individual Islands

`r render_figure("Figure App.F.12.3.", "../img/cinms_cr/App.F.12.3.Pochraceus_size.jpg")`

`r get_figure_info("Figure App.F.12.3.")`