---
output: html_document
editor_options: 
  chunk_output_type: console
---

```{r setup, include=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F, error=F)
library(magrittr)

# Let's pull the nms4r package from github, but only if it isn't already installed. We don't want to
# pull the package unnecessarily as github allows a max of 60 unauthenticated requests per hour.
ip = installed.packages()[,1]
if (all(ip!="nms4r")){
  library(devtools)
  devtools::install_github("marinebon/nms4r")
}

# The following is used by the plot_intertidal_nms function called later
dir_gdrive <- "/Volumes/GoogleDrive/Shared drives/NMS/data"
dir_pfx     <- file.path(dir_gdrive, "github_info-intertidal_data")
d_csv       <- file.path(dir_pfx, "sanctuary_species_percentcover.csv")
nms_rgns_csv    <- file.path(dir_pfx, "MARINe_graphs.xlsx - sites in regions.csv")
nms_rgns1 <- readr::read_csv(nms_rgns_csv) %>% 
  tidyr::fill(nms) %>% 
  dplyr::group_by(nms) %>% 
  tidyr::fill(region) %>% 
  dplyr::mutate(
    rgn = region) # View(nms_rgns)
```

`r nms4r::get_modal_info()`

##  {.tabset} 

### MARINe: Map of Sites

`r nms4r::get_figure_info("Figure App.F.12.2.")`

```{r map sites}
nms4r::map_nms_sites("cinms")
```

`r nms4r::md_caption("Figure Ux.Rocky.MARINe.map.")`

`r nms4r::md_caption("Figure Ux.Rocky.MARINe.map.", get_details = T, fig_in_report = F)`

### MARINe: Ochre Seastar (_Pisaster ochraceus_) {.active}

`r nms4r::get_figure_info("Figure App.F.12.2.")`

```{r plot seastar}
nms_spp_sscount_csv     <- file.path(dir_pfx, "sanctuary_species_sscount.csv")
nms4r::plot_intertidal_nms(nms_spp_sscount_csv, "CINMS", "PISOCH", "Ochre Seastar", nms_rgns1, fld_val = "count", label_y = "Count (annual avg)")
```

`r nms4r::md_caption("Figure Ux.Rocky.MARINe.Ochre-Stars.")`

`r nms4r::md_caption("Figure Ux.Rocky.MARINe.Ochre-Stars.", get_details = T, fig_in_report = F)`

### CHIS: Ochre Seastars across the sanctuary

`r nms4r::render_figure("Figure App.F.12.2.", "../img/cinms_cr/App.F.12.2.Pochraceus_abundance.jpg")`

### CHIS: Ochre Seastars at Individual Islands

`r nms4r::render_figure("Figure App.F.12.3.", "../img/cinms_cr/App.F.12.3.Pochraceus_size.jpg")`

`r nms4r::get_figure_info("Figure App.F.12.3.")`