
```{r, include=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F, error=F)
```

```{r svg, child = '_key-climate-ocean.Rmd'}
```

# {.tabset}
## Temperature {.tabset}
### Map: Satellite-based SST (CoastWatch)

```{r sst_map}
# get most recent date
date_end <- nms4r::get_dates(sst)[2]

leaflet(
  nms_ply,
  options = leafletOptions(
    crs = leafletCRS(crsClass = "L.CRS.EPSG4326"))) %>%
  # basemap from GBIF in 4326
  addTiles("//tile.gbif.org/4326/omt/{z}/{x}/{y}@1x.png?style=gbif-geyser") %>%
  # sst
  addWMSTiles(
    baseUrl = 'https://coastwatch.pfeg.noaa.gov/erddap/wms/jplMURSST41mday/request?',
    layers = "jplMURSST41mday:sst",
    options = WMSTileOptions(
      version = "1.3.0", format = "image/png", transparent = T, opacity = 0.7,
      time = format(date_end,"%Y-%m-%dT00:00:00Z")))  %>%
  addPolygons() %>%
  addMouseCoordinates() %>%
  leaflet::addLegend(
    position="bottomright",
    title = paste0("SST (°C)<br>", format(date_end,"%Y-%m-%d")),
    colorNumeric("Spectral", c(0,32), reverse=T), seq(0,32))
```

`r nms4r::md_caption("Figure Ux.Ocean.SST.ERD.map.")`

`r nms4r::md_caption("Figure Ux.Ocean.SST.ERD.map.", get_details = T, fig_in_report = F)`



### Trend: Satellite-based SST (CoastWatch)

```{r sst_time_series}
csv_SST <-here(glue("data/oceano/statistics_sst_{nms}.csv"))
url_SST  <- glue("https://github.com/marinebon/{nms}/raw/master/data/oceano/{basename(csv_SST)}")
html_SST <- a(basename(csv_SST), href=url_SST, target='_blank')
nms4r::plot_metric_timeseries(csv_SST, "sst")
```

`r nms4r::md_caption("Figure Ux.Ocean.SST.ERD.timeseries.")`

`r nms4r::md_caption("Figure Ux.Ocean.SST.ERD.timeseries.", get_details = T, fig_in_report = F)`

Download timeseries data for sanctuary: `r html_SST`


## Acidification {.tabset}
#### Aragonite saturation

`r nms4r::render_figure("Figure App.E.10.29.", "../img/cinms_cr/App.E.10.29.jpg")`

## Harmful Algal Blooms {.tabset}

#### Trends: Domoic Acid Levels (2012-13)

`r nms4r::render_figure("Figure App.D.7.1.", "../img/cinms_cr/App.D.7.1_DA levels in crustaceans and bivalves in 2012 and 2013_C. Culver CA Sea Grant copy.jpg")`

#### Map: Harmful Algal Bloom (2015)

`r nms4r::render_figure("Figure App.D.7.3.", "../img/cinms_cr/App.D.7.3_2015 HAB_McCabe et al. 2016.jpg")`

## Chlorophyll {.tabset}

### Map: Satellite-based (CoastWatch)
```{r chlorophyll_map}
# get most recent date
d_2 <- nms4r::get_dates(chl)[2]

leaflet(
  nms_ply,
  options = leafletOptions(
    crs = leafletCRS(crsClass = "L.CRS.EPSG4326"))) %>%
  # basemap from GBIF in 4326
  addTiles("//tile.gbif.org/4326/omt/{z}/{x}/{y}@1x.png?style=gbif-geyser") %>%
  # sst
  addWMSTiles(
    baseUrl = 'https://coastwatch.pfeg.noaa.gov/erddap/wms/nesdisVHNSQchlaMonthly/request?',
    layers = "nesdisVHNSQchlaMonthly:chlor_a",
    options = WMSTileOptions(
      version = "1.3.0", format = "image/png", transparent = T, opacity = 0.7,
      time = format(d_2,"%Y-%m-%dT00:00:00Z")))  %>%
  addPolygons() %>% 
  addMouseCoordinates() %>%
  leaflet::addLegend(
    position="bottomright",
    title = paste0("CHL (mg m^-3)<br>", format(d_2,"%Y-%m-%d")),
    colorNumeric("Spectral", c(0,4), reverse=T), seq(0,4))
```

`r nms4r::md_caption("Figure Ux.Ocean.Chl.ERD.map.")`

`r nms4r::md_caption("Figure Ux.Ocean.Chl.ERD.map.", get_details = T, fig_in_report = F)`
### Trend: Satellite-based (CoastWatch)

```{r chlorophyll_time_series}
csv_chl <-here(glue("data/oceano/statistics_chl_{nms}.csv"))
url_chl  <- glue("https://github.com/marinebon/{nms}/raw/master/data/oceano/{basename(csv_chl)}")
html_chl <- a(basename(csv_chl), href=url_chl, target='_blank')
nms4r::plot_metric_timeseries(csv_chl, "chl")
```

`r nms4r::md_caption("Figure Ux.Ocean.Chl.ERD.timeseries.")`

`r nms4r::md_caption("Figure Ux.Ocean.Chl.ERD.timeseries.", get_details = T, fig_in_report = F)`

Download timeseries data for sanctuary: `r html_chl`



## Nutrients {.tabset}

### Trend: Nitrate profile (PnB)

`r nms4r::render_figure("Figure App.D.6.5.", "../img/cinms_cr/App.D.6.5.png")`

### Trend: Phosphate profile (PnB)

`r nms4r::render_figure("Figure App.D.6.6.", "../img/cinms_cr/App.D.6.6.png")`

### Trend: Nitrate anomaly

`r nms4r::render_figure("Figure App.D.6.7.", "../img/cinms_cr/App.D.6.7_SST and nitrate anomalies 2001-2015_Reed et al._2016.jpg")`


## Basin Scale Indicies
### Trend: ONI, PDO, NPGO

`r nms4r::render_figure("Figure App.D.8.3.", "../img/cinms_cr/App.D.8.3.png")`