```{r, include=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F, error=F)
# Let's pull the nms4r package from github, but only if it isn't already installed. We don't want to
# pull the package unnecessarily as github allows a max of 60 unauthenticated requests per hour.
ip = installed.packages()[,1]
if (all(ip!="nms4r")){
  library(devtools)
  devtools::install_github("marinebon/nms4r")
}
```

```{r modal_info}
nms4r::get_modal_info()
```

# {.tabset}

## Human Activities

### {.tabset}

#### Oil & Gas {.tabset}

##### Trends: Offshore Oil and Gas Activity 

`r nms4r::render_figure("Figure App.C.4.17.", "../img/cinms_cr/App.C.4.17.Oil_gas_activity_CCIEA.png")`

##### Oil & Gas Maps {.tabset}

###### Offshore Oil Platforms

`r nms4r::render_figure("Figure App.C.2.1.", "../img/cinms_cr/App.C.2.1 Oil platforms_Mari Cajandig.jpg")`

###### 2015 Refugio Oil Spill

`r nms4r::render_figure("Figure App.C.2.3.", "../img/cinms_cr/App.C.2.3 Refugio Spill_Mari Cajandig.jpg")`

`r nms4r::render_figure("Figure App.C.2.4.", "../img/cinms_cr/App.C.2.4.jpg")`

`r nms4r::render_figure("Figure App.C.2.5.", "../img/cinms_cr/App.C.2.5.jpg")`

#### Vessel Traffic

##### {.tabset}

###### Map: Vessel Groundings

`r nms4r::render_figure("Figure App.C.3.1.", "../img/cinms_cr/App.C.3.1_VesselGroundingsMap.jpg")`

#### Visitors

##### {.tabset}

###### Trends: Visitors at Frenchy's Cove

`r nms4r::render_figure("Figure App.C.4.8.", "../img/cinms_cr/App.C.4.8.Visitation_Frenchys.jpg")`

###### Map: Location Recreational Activity

`r nms4r::render_figure("Figure App.C.4.7.", "../img/cinms_cr/App.C.4.7_chen_recreation.jpg")`

###### Trends: Visitors (CHIS)

`r nms4r::render_figure("Figure App.C.1.4.", "../img/cinms_cr/App.C.1.4.Vistors_CINP.png")`

#### Research
###### Trends: Active Permits

`r nms4r::render_figure("Figure App.C.4.18a.", "../img/cinms_cr/App.C.4.18a.Projects_Permits.png")`

`r nms4r::render_figure("Figure App.C.4.18b.", "../img/cinms_cr/App.C.4.18b.CDFW_Permits.png")`

## Human Impacts

### {.tabset}

#### Contaminants 
##### Contaminants in Mussels {.tabset}

###### Trends: Arsenic

`r nms4r::render_figure("Figure App.E.11.2.", "../img/cinms_cr/App.E.11.2.jpg")`

###### Trends: Iron

`r nms4r::render_figure("Figure App.E.11.3.", "../img/cinms_cr/App.E.11.3.jpg")`

###### Trends: Silver

`r nms4r::render_figure("Figure App.E.11.4.", "../img/cinms_cr/App.E.11.4.jpg")`

###### Trends: Heavy metals

`r nms4r::render_figure("Figure App.E.11.5.", "../img/cinms_cr/App.E.11.5.jpg")`

###### Trends: PAHs

`r nms4r::render_figure("Figure App.E.11.6.", "../img/cinms_cr/App.E.11.6.jpg")`

#### Seabird disturbance

##### Comparison: By Region

`r nms4r::render_figure("Figure App.C.4.9.", "../img/cinms_cr/App.C.4.9.Seabird_disturbance_rates_Robinette.jpg")`