
```{r setup, include=F}
knitr::opts_chunk$set(echo=F, message=F, warning=F, error=F)
library(infographiqR) # remotes::install_github("marinebon/infographiqR") 
library(onmsR) # remotes::install_github("noaa-onms/onmsR")
```

```{r svg, child = '_key-climate-ocean.Rmd'}
```

# {.tabset}
## Temperature {.tabset}
### Map: Satellite-based SST

```{r sst_map}
# get most recent date
date_end <- onmsR::get_dates(sst)[2]

leaflet(
  nms_ply,
  options = leafletOptions(
    crs = leafletCRS(crsClass = "L.CRS.EPSG4326"))) %>%
  # basemap from GBIF in 4326
  addTiles("//tile.gbif.org/4326/omt/{z}/{x}/{y}@1x.png?style=gbif-geyser") %>%
  # sst
  addWMSTiles(
    baseUrl = 'https://coastwatch.pfeg.noaa.gov/erddap/wms/jplMURSST41mday/request?',
    layers = "jplMURSST41mday:sst",
    options = WMSTileOptions(
      version = "1.3.0", format = "image/png", transparent = T, opacity = 0.7,
      time = format(date_end,"%Y-%m-%dT00:00:00Z")))  %>%
  addPolygons() %>% 
  addMouseCoordinates() %>%
  leaflet::addLegend(
    position="bottomright",
    title = paste0("SST (°C)<br>", format(date_end,"%Y-%m-%d")),
    colorNumeric("Spectral", c(0,32), reverse=T), seq(0,32))
```

`r infographiqR::md_caption("Figure Ux.Ocean.SST.ERD.map.")`

`r infographiqR::md_caption("Figure Ux.Ocean.SST.ERD.map.", get_details = T, fig_in_report = F)`

### Trend: Satellite-based SST 

```{r sst_time_series}
csv_SST <- here::here(glue::glue("data/oceano/statistics_sst_{nms}.csv"))
url_SST  <- glue::glue("https://github.com/marinebon/{nms}/raw/master/data/oceano/{basename(csv_SST)}")
html_SST <- htmltools::a(basename(csv_SST), href=url_SST, target='_blank')
onmsR::plot_metric_timeseries(csv_SST, "sst")
```

`r infographiqR::md_caption("Figure Ux.Ocean.SST.ERD.timeseries.")`

`r infographiqR::md_caption("Figure Ux.Ocean.SST.ERD.timeseries.", get_details = T, fig_in_report = F)`

Download timeseries data for sanctuary: `r html_SST`

### Trend: SST anomaly

```{r sst anomaly time series}
csv_SST <-here::here(glue::glue("data/oceano/sst_anomaly_{nms}.csv"))
url_SST  <- glue::glue("https://github.com/marinebon/{nms}/raw/master/data/oceano/{basename(csv_SST)}")
html_SST <- htmltools::a(basename(csv_SST), href=url_SST, target='_blank')
onmsR::plot_SST_anomaly(csv_SST)
```

`r infographiqR::md_caption("Figure Ux.Ocean.SST.Anomaly.timeseries.")`

`r infographiqR::md_caption("Figure Ux.Ocean.SST.Anomaly.timeseries.", get_details = T, fig_in_report = F)`

Download timeseries data for sanctuary: `r html_SST`
